---
title: "Ratemybeer"

output: html_document
---

This is a Rmarkdown version of the project Ratemybeer.

Initially we have uploaded all the libraries which is necessary for working on the project

```{r}
library(rvest)
library(XML)
library(gsubfn)
```

This first section of the code is actually utlizzing css selector for web mining and extract data of our interest.  The same has been created into the dataframe.

```{r, echo=TRUE}
page = read_html("https://www.ratebeer.com/beer/top-50/")
first_column = html_nodes(page,".orange+ td a")
name = html_text(first_column)
beer_url = html_attrs(first_column)
url = paste0("https://www.ratebeer.com/",beer_url)
score = html_text(html_nodes(page,"#tablecontent b"))
count1 = html_text(html_nodes(page,"font"))
count = gsub("\\s+", "", count1)
style = html_text(html_nodes(page,"td:nth-child(6) a"))
df = data.frame(name, url, count, score, style, stringsAsFactors = F) 
head(df,4)
```

In this section, we have done subseting of the data based on count >500.
We received 23 beer which has a count of more than 500.

One interesting insight came out that the beer which as rated number 1 does not feature in the top beer havung count of more than 500.

```{r, echo=TRUE}
df$count = as.numeric(df$count)
df1 = subset(df, count>500)
table = df1[order(df1$count, decreasing = TRUE),]
```

In this section, we have scarped web data like seasonality, brewed by etc for each beer own web page and stored in a dataframe beer_table.   We have merged two datafrem and result are store in table1.  

```{r, echo=TRUE}
#Extracting other information attributes about the beer
beer_table <- NULL
for (row in 1:nrow(table)){
  page1=table$url[row]
text <- read_html(page1) %>% 
  html_nodes("#container > div.row.columns-container > div.col-sm-8 > div.stats-container > small") %>% 
  html_text()
beer_table$brewedby[row] <- read_html(page1) %>% html_nodes("#_brand4 span") %>% html_text()
beer_table$Ratings[row] <- gsub("\\s+","", strsplit(strsplit (text, "RATINGS: ")[[1]][2], " ")[[1]][1])
beer_table$Seasonal[row] <- gsub("\\s+","", strsplit(strsplit (text, "SEASONAL: ")[[1]][2], " ")[[1]][1])
beer_table$Weighted_Avg[row] <- gsub("\\s+","", strsplit(strsplit (text, "WEIGHTED AVG: ")[[1]][2], " ")[[1]][1])
beer_table$Calorie[row] <- gsub("\\s+","", strsplit(strsplit (text, "EST. CALORIES: ")[[1]][2], " ")[[1]][1])
beer_table$ABV[row] <- gsub("\\s+","", strsplit(strsplit (text, "ABV: ")[[1]][2], " ")[[1]][1])
beer_table$commercial_description[row] <- read_html(page1) %>% html_nodes("#_description3") %>% html_text()
}

beer_table<-as.data.frame(beer_table, stringsAsFactors=FALSE)

# Merging the two data frame by ratings/count
table1 = merge(beer_table,table, by.y = "count", by.x = "Ratings")
table1$Ratings = as.numeric(table1$Ratings)
table1=table1[order(table1$Ratings,decreasing = TRUE),]

#Arranging rows for better depiction
table1= table1[c(8,4,2,3,1,5,6,9,7)]

```
In this section, we have scarped web data like aroma, rating, palate etc and reviews upto 3 pages for each beer.  The result is saved as list1 for each beer.
1.As a first step, i have extracted review container as  a whole and strip text based on Aroma, Palate etc.
2.As a second step, Ratings have been extracted.
3.As third step different CSS selector was used to extract reviews.  The reviews were stored in List and have been extrcated and stored in a character vector.
4.FInally, all the information have been stored as a data frame in "table3" and as a List in "List1".

```{r, echo=TRUE}
# now for each beer extract the data
list1 = list()
table3 = NULL
for (c in 1:nrow(table1)){
  table2 = NULL
  u = table1$url[c]
  for (j in 1:3) {
    u1 = paste0(u,"1/",j,"/")
    reviews <- read_html(u1) %>% html_nodes(".reviews-container") %>% html_text()
    Aroma = gsub("AROMA|/10| ","",strapplyc(reviews,"AROMA [0-9]/10|AROMA [0-9][0-9]/10")[[1]])
    Appearance = gsub("APPEARANCE|/5| ","",strapplyc(reviews,"APPEARANCE [0-5]/5")[[1]])
    Taste = gsub("TASTE|/10| ","",strapplyc(reviews,"TASTE [0-9]/10|TASTE [0-9][0-9]/10")[[1]])
    Palate = gsub("PALATE|/5| ","",strapplyc(reviews,"PALATE [0-5]/5")[[1]])
    Overall = gsub("OVERALL|/20| ","",strapplyc(reviews,"OVERALL [0-9]/20|OVERALL [0-9][0-9]/20")[[1]])
    Ratings <- read_html(u1) %>% html_nodes(".reviews-container div+ div") %>% html_text() %>% as.numeric()
    review_container <- read_html(u1) %>% html_nodes(".reviews-container br+ div") %>% html_text()
    Review = NULL
    i=1
    for (k in c(seq(1,9,2), seq(10,18,2))){
      Review[i] <- review_container[k]
      i=i+1}
    new <-  data.frame(Aroma, Appearance, Taste, Palate, Overall,Ratings, Review)
    table2 <- rbind(table2, new)
  }
  table2$url = u
  table2$Name = table$name[c]
  table3 = rbind(table3, table2)
  list1[[table$name[c]]] = table2
}

```

